---
title: "tidy-model"
output: html_document
---
## Introduction

This R Markdown document demonstrates my abilities to use models for data analysis using a data set collected on crickets.
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library('tidyverse') ; library('modeldata')
``` 

```{r load data, include = FALSE}
data(crickets, package = "modeldata")
names(crickets)
```

## What is that sound?
In this report, we examine what factors predict a cricket's chirp rate.

```{r summary, echo = FALSE}
summary(crickets)
ggplot(crickets, aes(x = rate,fill = species)) +
  geom_histogram(bins = 8) + 
  ggtitle("Distribution of the chirp rate of crickets") +
  xlab('Chirp rate (per min.)')
```

There is 14 exclamations and 17 niveus. The minimum temperature is 17.20, and the maximum temperature is 30.40. The mean rate of chirping is 72.89 

## Temperature affects chirp rate

```{r temp, echo= FALSE}
ggplot(crickets, aes(x = temp, y = rate)) +
  geom_point() + 
  geom_smooth(method = 'lm') +
  ggtitle("Plot of temperature and chirp rate") +
  ylab('Chirp rate (per min.)') +
  xlab('Temperature (Celsius)')

temp_lm <- lm(rate ~ temp, crickets)

summary.lm(temp_lm)
```

Based on a scatter plot of temperature and chirping and a correlation test, it seems that as temperature increases one degree, the rate of chirping increases about 4.2 chirps per minute.

## Species-specific effects of temperature on chirping
```{r species, echo= FALSE}
ggplot(crickets, aes(x = temp, y = rate, color = species)) +
  geom_point() + 
  geom_smooth(method = 'lm') +
  ggtitle("Plot of temperature and chirp rate for two species of crickets") +
  ylab('Chirp rate (per min.)') +
  xlab('Temperature (Celsius)')
  
  
species_lm <- lm(rate ~ temp + species, crickets)

summary.lm(species_lm)
```

The exclamations have a higher chirp rate and a greater maximum temperature. Niveus chirp rate is greater at lower temperatures.

## Interactions

```{r interactions, echo= FALSE}
ggplot(crickets, aes(x = temp, y = rate, color = species)) +
  geom_point() + 
  geom_smooth(method = 'lm') +
  ggtitle("Plot of temperature and chirp rate for two species of crickets") +
  ylab('Chirp rate (per min.)') +
  xlab('Temperature (Celsius)')
  
species_x_temp_lm <- lm(rate ~ temp + species + temp:species, crickets) 
summary.lm(species_x_temp_lm)

anova(species_lm, species_x_temp_lm)
```

## Load the data
```{r diamonds, echo=FALSE}
library(ggplot2)

data(diamonds)  
head(diamonds) 
```

## Distribution of the price 
```{r prices, echo=FALSE}
ggplot(diamonds, aes(x = price)) +
  geom_histogram(bins = 50, fill = "blue", color = "black") +
  ggtitle("Distribution of Diamond Prices") +
  xlab("Price") +
  theme_minimal()


``` 